# Guide to Co-Authors and Editors {-}


## Stages of Work and Milestones {-}


### Proposed Schedule {-}

- March 4 Updated Outline
- March 5 Writing Partners
- March 20 Draft Text
- March XX Peer Review
- April XX Revision
- May X 5, Submission for Grading


## Revision History and Process {-}

### Publication Dates {-}

I will regularly push and publish the results of the text based on submissions. 



### Using R Markdown {-}





### Basic Text Options

The most often used text options are for superscripts (which have ^) used on both sides of scripted. And for subscripts, we use ~ on both sides of the text to be scripted.

For example, NH~4~^+^ has both!


### Using R to Create Figures {-}{#createfigure}

R Markdown can be a very powerful tool to integrate R code, figures and text. Making high quality figures that are both clear and aestically pleasing will be something that we need to think about it. 

- Axis Labels -- Labelled with clarity 
- Axis Text -- Size, Orientation 
- Captions (usually better than titles)
- References connecting labels to references
- ADA accessible (e.g. color impairment mitigation)

```{r, updatedmaunaloa, echo=FALSE, results='hide', eval=FALSE}
address <- "ftp://aftp.cmdl.noaa.gov/products/trends/co2/co2_mm_mlo.txt"
download.file(address, "maunaloa", quiet = F, mode = "w", cacheOK = T)

maunaloa <- read.table("maunaloa", skip=70)
names(maunaloa) <- c("year", "month", "decimal.date", "average", "interpolated", "trend", "days")
maunaloa$average[maunaloa$average==-99.99] <- NA
maunaloa <- data.frame(year=maunaloa$year, month=maunaloa$month, decimal.date=maunaloa$decimal.date, average=maunaloa$average)
head(maunaloa)
str(maunaloa)
write.csv(maunaloa, file = "/home/CAMPUS/mwl04747/github/Environmnental-Sciences-in-East-Asia/data/maunaloa.csv", eol = "\n", row.names = F)
```

```{r, analyzingdata, echo=FALSE, results=FALSE, warning=FALSE, message=FALSE}
maunaloa = read.csv("/home/CAMPUS/mwl04747/github/Environmnental-Sciences-in-East-Asia/data/maunaloa.csv")
library(dplyr)
library(tidyverse)
library(caret)
library(mgcv)

# Split the data into training and test set
set.seed(123)
training.samples <- maunaloa$average %>%
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- maunaloa[training.samples, ]
test.data <- maunaloa[-training.samples, ]
future.data = max(maunaloa$decimal.date)+1:36/12

# Build the model
model <- gam(average ~ s(decimal.date), data = maunaloa)
summary(model)
# Make predictions
predictions <- model %>% predict(test.data)
# Model performance
data.frame(
  RMSE = RMSE(predictions, test.data$average),
  R2 = R2(predictions, test.data$average)
)
```

In the case of Figure \@ref(fig:maunaloa), we can a create a figure that has all of the characteristics listed above, except perhaps ADA. Creating a "alt text" for the figure is something we might want to consider. 

```{r, maunaloa, echo=FALSE, fig.cap='Carbon Dioxide Concentrations (Mauna Loa, HI). Source: Scripps/NOAA.'}
theme_set(theme_classic())
ggplot(train.data, aes(decimal.date, average) ) + 
#  stat_smooth(method = lm, formula = y ~ poly(x, 3, raw = TRUE), fullrange=T) +
  geom_line() + xlab("Year") + ylab("Carbon Dioxide (ppm)") +
  stat_smooth(method = gam, formula = y ~ s(x), color = "red") +
  theme(axis.text.x = element_text(size=14),
          axis.text.y = element_text(size=14), 
          axis.title=element_text(size=14))

```

### Citations and Cross-References {-}

We can cross-reference sections (e.g. Section \@ref(earthsystem))  or figures (Figure \@ref(fig:maunaloa)) using several methods. I suggest you look at the this Rmd file to see how I did it in these examples.

There will be two steps to cite our sources. First, we need to add the reference to a database, or bib file. This is titled 'references.bib' and is located in the bib folder in our respository. When you add information to the bib file, be sure to paste in the reference using a bibTeX format. 

Second, we'll need to place in-line citations, using ```[@ggplot2]```, which produces [@ggplot2], by using a key, which is ggplot2 in this case. 

## Acknowledgements {-}
